Lab News

### 2024-11-20 index.qmd
update news

@@

<font color="#d08770">[September 05 2023].</font> **New milestone**. Congratulations to Mikayla Lalli on successfully defending her MSc work. We are excited that Mikayla is staying in the lab for her doctoral studies.

@@

<font color="#d08770">[August 20 2024].</font> **New Preprint**. Calalo, J.A., Ngo, T.T., Sullivan, S.R., Strand, K., Buggeln, J.H., Lokesh, R., Roth, A.M., Carter, M.J, Kurtzer, I.L., & Cashaback, J.G.A. Online movements reflect ongoing deliberation. *bioR$\chi$iv*. [https://doi.org/10.1101/2024.08.19.608669](https://doi.org/10.1101/2024.08.19.608669){target="_blank"}

>>>>

<font color="#d08770">[October 21 2024].</font> **New milestone**. Congratulations to Nour Al Afif on successfully defending her MSc work. We are excited that Nour is staying in the lab for her doctoral studies.

@@

<font color="#d08770">[September 05 2024].</font> **New milestone**. Congratulations to Mikayla Lalli on successfully defending her MSc work. We are excited that Mikayla is staying in the lab for her doctoral studies.

@@
